How and Why to run a Hack Week

### 2017-12-05 sections/what.tex
a few sentences about summer school versus hack week

>>>>

Three design considerations distinguish the hack week from the summer school model: (1) hack week transfer knowledge across many levels of senority, with participants routinely leading tutorials, in part due to the relative newness of the content and the distributed knowledge base; (2) hack weeks contain a significant amount of unstructured time, creating the conditions for improvised exchanges and project development; and (3) hack weeks intentionally priortize participant diversity because this is known to maximize the liklihood for the co-creation of learning during the event.
